### 2017-07-05 README.Rmd
update ReadMe
Change to basic .yaml and add to Readme

@@

The goal of WetlandComparison is to ...

>>>>

[![Travis-CI Build Status](https://travis-ci.org/samdchamberlain/WetlandComparison.svg?branch=master)](https://travis-ci.org/samdchamberlain/WetlandComparison)

@@

The goal of WetlandComparison is to make a first attempt at a reproducible research R package. This will still be somewhat hampered by the fact that much of this research is conducted with Matlab.
